An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-08-05 EconGrowth2.Rnw
Added details about how many unconverged LINEX models are present to the text using \Sexpr.

\noindent where $a_1 \equiv a_0 c_t$. 
We used the \texttt{nls} function in \texttt{R}
\citep{R} to estimate least-squares values for $a_0$ and $a_1$ in 
Equation~\ref{eq:LINEX_transformed}. We recovered
a value for $c_t$ with $c_t = a_1 / a_0$. The reparameterization
of Equation~\ref{eq:LINEX_transformed} reduced the number of 
unconverged resample fits to nearly zero.

>>>>

\noindent where $a_1 \equiv a_0 c_t$. 
We used the \texttt{nls} function in \texttt{R}
\citep{R} to estimate least-squares values for $a_0$ and $a_1$ in 
Equation~\ref{eq:LINEX_transformed}. We recovered
a value for $c_t$ with $c_t = a_1 / a_0$. The reparameterization
shown in Equation~\ref{eq:LINEX_transformed} reduced the number of 
unconverged resample fits to nearly zero: 
The largest fraction of unconverged resample fits is found 
for Zambia (ZM) with thermal energy ($q$), where
\Sexpr{fracUnconvergedResampleFits(modelType="linex", countryAbbrev="ZM", energyType="Q")*100}\%
of the resample fits did not converge. 
(See Table~\ref{tab:frac_unconverged_models}.)
